### 2015-01-14 src/methodology.Rnw
update abstract
update methodology

\section{Methodology} \label{sec:methodology} Our selection of
programs was driven by a few overriding concerns. Our primary
requirement was that our results had to be as widely applicable as
possible for real-world programs. Secondly, we strived for a
statistically significant result, reducing the number of variables
present in the experiments. For this reason we chose a random sample
of Java projects from Github~\cite{github} that use the popular
maven~\cite{maven} build system, following the methodology we used
previously in an ICSE 2014 paper~\cite{gopinath2014code}. As in that
work, we utilize two kinds of of test suites: the original test suites
present in a limited number of projects, and automatically generated
test suites from Randoop~\cite{randoop}. From this set of test suites,
After eliminating those that took too long to finish, we sampled 107
suites each for both original and Randoop generated test suites,
Since there was some overlap between projects with
original test suites, and those with generated test suites, we had 81
unique projects each in both sets. The remaining 26 projects had both
flavors of test suites.

@@

For a detailed description of each mutation operator, please refer to PIT documentation~\cite{pitmut}.
PIT was also modified to provide random selection of mutants according
to various criteria.
Finally, to remove random noise, each criteria
described was run four times, and the results averaged to produce
the final result.

@@

We used several different sampling criteria, some of which has been suggested
in the literature before, some which are variants of previously suggested
criteria, and a few novel ones.  For each sampling
criteria, we sampled mutants on a decreasing power scale, sampling
\textit{1/2, 1/4, 1/8, 1/16, 1/32, 1/64} of the total mutants.

@@

\subsubsection{One per element}
Another simple strategy of sampling we experimented with is to just choose
one mutant per program element, in the order \textit{line}, \textit{method}, \textit{class}.

@@

\subsubsection{N-selection}
\noindent\textbf{Offut et al. ~\cite{offutt1993experimental}.} They suggested removal of
$n$ most numerous operators. In our experiment, the order of operators was
\Pitnvmc, \Pitnc, \Pitrc, \Pitdc, \Pitrv, \Pitic, \Pitcc, \Pitemv, \Pitvmc,
\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin. We discarded one at each
step and evaluated the effectiveness at each $n$.
%----------------------------------------
\subsubsection{Statement Deletion} \label{subsec:stmtdel} The basic
statement deletion was modeled on the work by Deng et
al.~\cite{deng2013empirical}. The operations on single statements were
modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and \Pitri~for
simple statements, and using \pitrc for control structures. \pitrc
replaces boolean conditions with \textit{false}, resulting in removal of the
conditional block. The operator for return values was modeled using
\Pitrv, which is similar.  The operators for \textit{while},
\textit{for}, and \textit{if} statements were modeled using \Pitdc,
which replaced the boolean condition with \textit{true}, which removed the
effect of conditional. The \textit{switch} statement deletion was
modeled using \pitrs which replaced the first 100 labels with a
\textit{default} label, resulting in the switch element being
deleted. Due to the constraints of the architecture of PIT only the
first 100 labels were replaced. Deleting \textit{try/catch} was not
necessary at bytecode level.  Finally, to get an accurate estimation
of the effect of true statement deletion, we grouped the mutants by
line, and considered each line a single virtual mutant (that is, the total
number of mutants is equal to the total number of lines). Further,
killing any mutant from a line resulted in marking the virtual mutant
for that line as killed. This gave us the mutation score for the
virtual statement deletion operator.  We note that the approximation
of simple statement deletion, especially when arithmetic operators are
involved, is not complete. However,
the number of mutants produced by \pitm operator is very small. We
also note that our approximation does not account for the increase in
ease of detection when multiple mutations are combined together due to
the coupling effect. This also means that not all the lines may be
mutated ,since there may be no applicable operators. However, given
the constraints of a bytecode based mutation system, we believe that
our procedure is reasonable.
% An interesting point is that using this
%procedure statement, deletion is no longer a simple mutation and
%qualifies as a higher order mutation operator. In fact, the procedure
%we outlined can be used in general to judge the effectiveness of a
%higher order operator from the results of the first order mutation
%operators that together compose the higher order mutant.

>>>>

\section{Methodology} \label{sec:methodology} Our selection of
programs was driven by a few overriding concerns. Our primary
requirement was that our results had to be as widely applicable as
possible for real-world programs. Secondly, we strived for a
statistically significant result, reducing the number of variables
present in the experiments. For this reason we chose a random sample
of Java projects from Github~\cite{github} and Apache Software
Foundation~\cite{apache} that use the popular
maven~\cite{maven} build system, following the methodology we used
previously in an ICSE 2014 paper~\cite{gopinath2014code}.

@@

For a detailed description of each mutation operator, please refer to PIT documentation~\cite{pitmut}.
We modified PIT to report the entire test matrix of $tests \times failures$
rather than just the first failure, and used this for our analysis. To remove
the effects of random noice, results of each criteria was averaged out of ten
runs.

@@

We used several different sampling criteria that has been mentioned in the
literature, For each sampling criteria, we sampled mutants on a decreasing
power scale, sampling \textit{1/2, 1/4, 1/8, 1/16, 1/32, 1/64} of the total
mutants.

@@

@@

\subsubsection{N-selection}
\noindent\textbf{Offut et al. ~\cite{offutt1993experimental}.} They suggested removal of
$n$ most numerous operators. In our experiment, the order of operators was
\Pitnvmc, \Pitrv, \Pitic, \Pitdc, \Pitnc, \Pitrc, \Pitvmc, \Pitcc, \Pitemv,
\Pitm, \Pitcb, \Piti, \Pitri, \Pitrs, \Pites, and \Pitin
We discarded one at each
step and evaluated the effectiveness at each $n$.
%----------------------------------------
\subsubsection{Statement Deletion} \label{subsec:stmtdel} The basic
statement deletion was modeled on the work by Deng et
al.~\cite{deng2013empirical}. The operations on single statements were
modeled using \Pitvmc, \Pitnvmc, \Pitcc, \Pitemv, and \Pitri~for
simple statements, and using \pitrc for control structures. \pitrc
replaces boolean conditions with \textit{false}, resulting in removal of the
conditional block. The operator for return values was modeled using
\Pitrv, which is similar.  The operators for \textit{while},
\textit{for}, and \textit{if} statements were modeled using \Pitdc,
which replaced the boolean condition with \textit{true}, which removed the
effect of conditional. The \textit{switch} statement deletion was
modeled using \pitrs which replaced the first 100 labels with a
\textit{default} label, resulting in the switch element being
deleted. Due to the constraints of the architecture of PIT only the
first 100 labels were replaced. Deleting \textit{try/catch} was not
necessary at bytecode level.  Finally, to get an accurate estimation
of the effect of true statement deletion, we grouped the mutants by
line, and considered each line a single virtual mutant (that is, the total
number of mutants is equal to the total number of lines). Further,
killing any mutant from a line resulted in marking the virtual mutant
for that line as killed. This gave us the mutation score for the
virtual statement deletion operator.  We note that the approximation
of simple statement deletion, especially when arithmetic operators are
involved, is not complete. However,
the number of mutants produced by \pitm operator is very small. We
also note that our approximation does not account for the increase in
ease of detection when multiple mutations are combined together due to
the coupling effect. This also means that not all the lines may be
mutated ,since there may be no applicable operators. However, given
the constraints of a bytecode based mutation system, we believe that
our procedure is reasonable.
% An interesting point is that using this
%procedure statement, deletion is no longer a simple mutation and
%qualifies as a higher order mutation operator. In fact, the procedure
%we outlined can be used in general to judge the effectiveness of a
%higher order operator from the results of the first order mutation
%operators that together compose the higher order mutant.
